%-------------------------
% Resume in Latex
% Author : Jake Gutierrez (Adapted for Akshit Soni)
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{ragged2e} % For justified text
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins unchanged from previous version (~0.5in on both sides)
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\setlength{\tabcolsep}{-5in}

% Sections formatting with reduced spacing
\titleformat{\section}{
  \vspace{-13pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands with reduced spacing
\newcommand{\resumeItem}[1]{
  \item\small{
    \justify{#1} \vspace{-0.9pt}
  }
}

% Single-column subheading with right-aligned date/location
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{flushleft}
    \textbf{#1} \hfill #2 \\
    \textit{\small#3} \hfill \textit{\small #4}
  \end{flushleft}\vspace{-1pt}
}

% For university with CGPA on next line
\newcommand{\resumeSubheadingWithCGPA}[5]{
  \vspace{-1pt}\item
  \begin{flushleft}
    \textbf{#1} \hfill #2 \\
    \textit{\small#3} \hfill \textit{\small #4} \\
    \textit{\small#5}
  \end{flushleft}\vspace{-1pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.25in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3.4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Large \scshape Akshit Soni} \\ \vspace{1pt}
    \small +91 9358841182 $|$ \href{mailto:soniakshit15502@gmail.com}{\underline{soniakshit15502@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/akshit-soni-627745232/}{\underline{linkedin.com/in/akshit-soni-627745232}} $|$
    \href{https://github.com/Akshit-Soni}{\underline{github.com/Akshit-Soni}}
\end{center}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheadingWithCGPA
      {Vellore Institute of Technology, Bhopal}{Bhopal, Madhya Pradesh}
      {Integrated MTech in Computer Science and Engineering - Artificial Intelligence}{Expected May 2026}
      {Cumulative CGPA: 8.32}
    \resumeSubheading
      {Tagore Public School}{Jaipur, Rajasthan}
      {12\textsuperscript{th} CBSE Board: 88.20\%}{March 2019 -- March 2020}
    \resumeSubheading
      {Tagore Public School}{Jaipur, Rajasthan}
      {10\textsuperscript{th} CBSE Board: 92.00\%}{}
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{CERTIFICATIONS}
  \resumeSubHeadingListStart
      \resumeItem{• Computer Vision - VITyarthi ~~~~~~~~~~~~~~~~~~~~~~~~ • Applied ML in Python - Coursera ~~~~~~~~~~~~~~~~~~~~~~~~ • Cloud Computing - NPTEL}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{TECHNICAL SKILLS}
  \resumeSubHeadingListStart
    \resumeItem{Python, Java, SQL, Office 365}
  \resumeSubHeadingListEnd

%-----------CO-CURRICULAR EXPERIENCE-----------
\section{CO-CURRICULAR EXPERIENCE}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AI Trainer | Freelancer}{Jaipur, Rajasthan (Remote)}
      {DataAnnotations Tech}{October 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Conducted comprehensive testing of LLM models across 200+ test cases from diverse domains, including brainstorming content, extraction, data generation, code generation, and math solving.}
        \resumeItem{Performed multilingual testing and evaluation across 5 parameters and in three languages, including English, Hindi (Devanagari), and Hindi (Latin), to enhance AI model localization and performance.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Crop Health Detection using Artificial Intelligence}{Bhopal, Madhya Pradesh}
      {University Level Project}{January 2024 -- April 2024}
      \resumeItemListStart
        \resumeItem{Implemented an AI-driven system to assess sugarcane crop health using advanced machine learning techniques, integrating 4 different models: DenseNet201, CNN, VGG19 and ResNet50.}
        \resumeItem{Achieved 92\% overall accuracy in detecting and classifying crop conditions, including disease, pest infestation, and nutrient deficiencies, by leveraging deep learning architectures.}
        \resumeItem{Reduced operational costs for farmers by an estimated 30\% through accurate early detection of diseases and targeted resource application.}
        \resumeItem{Collaborated with a team of 10 developers to develop and deploy a scalable AI solution adapted to sugarcane crop and geographic regions.}
      \resumeItemListEnd
    \resumeSubheading
      {Face Recognition}{Jaipur, Rajasthan}
      {Personal Project}{February 2022 -- February 2022}
      \resumeItemListStart
        \resumeItem{Developed a face recognition system using KNN and SVM algorithms by collecting a dataset of 400-500 images, ensuring optimal image data preprocessing for achieving accurate recognition results in real-time applications.}
        \resumeItem{Incorporated Python-based libraries for image evaluation and model training, gaining experience in fine-tuning outputs and managing input data.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXTRA CURRICULAR ACTIVITIES-----------
\section{EXTRA CURRICULAR ACTIVITIES}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vice President}{Bhopal, Madhya Pradesh}
      {Android Club, VIT Bhopal}{June 2023 -- May 2024}
      \resumeItemListStart
        \resumeItem{Led 10 teams (SDC, Android, Event Management, Design, Operations, Finance) to organize 7 events, boosting student engagement by 1500\% and mentoring 80+ club members to improve technical skills and communication.}
        \resumeItem{Streamlined workflows for 20\% higher efficiency and implemented feedback loops to enhance event quality and relevance.}
      \resumeItemListEnd
    \resumeSubheading
      {Discipline Committee Member}{Bhopal, Madhya Pradesh}
      {AdVITya Annual Fest, VIT Bhopal}{February 2024 -- February 2024}
      \resumeItemListStart
        \resumeItem{Managed discipline and coordinated logistics for Advitya Fest, which hosted 2500+ student participants and 50+ events across university clubs.}
        \resumeItem{Co-ordinated closely with faculties to ensure smooth execution, contributing to a well-organized and engaging festival experience.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------HOBBIES & INTERESTS-----------
\section{HOBBIES \& INTERESTS}
  \resumeSubHeadingListStart
    \resumeItem{Cooking | Space Enthusiast | Game Development | 3D Animation}
  \resumeSubHeadingListEnd

%-----------LANGUAGES-----------
\section{LANGUAGES}
  \resumeSubHeadingListStart
    \resumeItem{English - Highly Proficient | Hindi - Native}
  \resumeSubHeadingListEnd

\end{document}