%------------------------
% Resume in LaTeX
% Author : Shubham Rathod (Adapted from Jake Gutierrez)
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article} % Reduced font size

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{ragged2e}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1in}

\urlstyle{same}
\raggedbottom

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\normalsize
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1
\setlist[itemize]{itemsep=0pt, topsep=0pt} % Tighter list spacing

\newcommand{\resumeItem}[1]{\item\small{\justify{#1} \vspace{-1.5pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{flushleft}
    \textbf{#1} \hfill #2 \\
    \textit{\small#3} \hfill \textit{\small #4}
  \end{flushleft}\vspace{-1pt}
}
\newcommand{\resumeSubheadingWithCGPA}[5]{
  \vspace{-1pt}\item
  \begin{flushleft}
    \textbf{#1} \hfill #2 \\
    \textit{\small#3} \hfill \textit{\small #4} \\
    \textit{\small#5}
  \end{flushleft}\vspace{-1pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.25in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\begin{document}

\begin{center}
    \textbf{\Large \scshape Shubham Rathod} \\ \vspace{1pt}
    \small +91-8319450574 $|$ \href{mailto:Shubhamrathod1619@gmail.com}{\underline{Shubhamrathod1619@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/shubham-rathod-821a01202/}{\underline{linkedin.com/in/shubham-rathod}} $|$
    \href{https://github.com/Rathod-shubhamm}{\underline{github.com/Rathod-shubhamm}}
\end{center}

\section{EDUCATION}
\resumeSubHeadingListStart
  \resumeSubheadingWithCGPA
    {Vellore Institute of Technology, Bhopal}{Bhopal, Madhya Pradesh}
    {Integrated MTech in Artificial Intelligence}{August 2021 -- August 2026}
    {Cumulative CGPA: 7.79}
  \resumeSubheading
    {Shree Shankar School}{Dhamnod, Madhya Pradesh}
    {Class 12\textsuperscript{th} - 78.00\%, Class 10\textsuperscript{th} - 86.40\%}{March 2017 -- March 2020}
\resumeSubHeadingListEnd

\section{TECHNICAL SKILLS}
\resumeSubHeadingListStart
  \resumeItem{\textbf{Skills:} Python, R, SQL, Machine Learning, RAG, NLP, Agentic Workflows}
  \resumeItem{\textbf{Frameworks:} PyTorch,Tensorflow,  LangChain, React}
  \resumeItem{\textbf{Tools:} Git, VS Code, Framework, Jupyter, Pinecone, ChromaDB}
\resumeSubHeadingListEnd

\section{CERTIFICATIONS}
\resumeSubHeadingListStart
  \resumeItem{AWS Solutions Architect Associate \quad | \quad Data Analysis with Python - FreeCodeCamp}
  \resumeItem{Cloud Computing - NPTEL \quad | \quad Machine Learning with Python - FreeCodeCamp}
\resumeSubHeadingListEnd

\section{CO-CURRICULAR EXPERIENCE}
\resumeSubHeadingListStart
  \resumeSubheading
    {AI Trainer (Freelance)}{Bhopal, Madhya Pradesh (Remote)}
    {DataAnnotations Tech}{October 2024 - December 2024}
    \resumeItemListStart
      \resumeItem{Conducted 700+ structured test cases to rigorously evaluate Large Language Models (LLMs) across diverse NLP tasks including content generation, data extraction, coding assistance, ensuring high-quality deliverables.}
      \resumeItem{Delivered 500+ hours of prompt engineering, annotation, and iterative feedback, significantly improving model accuracy and minimizing hallucinations through data-driven insights.}
      \resumeItem{Led multilingual evaluations in English and Hindi (Devanagari and Latin scripts), applying five key parameters to enhance localization and user experience.}
      \resumeItem{Collaborated with remote cross-functional teams to document findings, identify edge cases, and refine AI model performance metrics, strengthening analytical reporting and communication.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{PROJECTS}
\resumeSubHeadingListStart
  \resumeSubheading
    {Agent AI Coding Assistant}{Bhopal, Madhya Pradesh}
    {Personal Project}{May 2025 -- Present}
    \resumeItemListStart

      \resumeItem{Engineered an AI coding assistant leveraging Retrieval-Augmented Generation (RAG) and ChromaDB to index 500+ code snippets, reducing hallucination rates by 45\% and improving output reliability.}
      \resumeItem{Applied ReAct prompt strategies to enhance Large Language Model (LLM) accuracy, achieving a 92\% success rate in resolving Python and JavaScript errors, increasing debugging efficiency.}
      \resumeItem{Integrated a hybrid precision@3 search pipeline within a custom VS Code extension, boosting suggestion relevance by 35\% and streamlining developer workflow.}
    \resumeItemListEnd

  \resumeSubheading
    {NoCap RAG - Context-aware document retriever}{Bhopal, Madhya Pradesh}
    {Personal Project}{January 2025 -- February 2025}
    \resumeItemListStart
      \resumeItem{Architected a document-aware Retrieval-Augmented Generation (RAG) system by integrating LangChain, Pinecone, and OpenAI APIs, increasing factual accuracy by 35\% and reducing hallucinations by 40\%.}
      \resumeItem{Designed and implemented a chatbot interface supporting queries on 1,000+ indexed documents, accelerating vector search retrieval by 20\% through prompt tuning and vector optimization.}
      \resumeItem{Utilized advanced NLP techniques such as chunking, embedding, and precision@k evaluation to enable scalable, real-time question and answer interactions, improving responsiveness.}
    \resumeItemListEnd

  \resumeSubheading
    {Crypto Tweet Tracker}{Bhopal, Madhya Pradesh}
    {Personal Project}{March 2025 -- April 2025}
    \resumeItemListStart
      \resumeItem{Developed a real-time monitoring tool using Twitter API v2 and Tweepy to track cryptocurrency mentions by verified influencers, maintaining 99\% uptime and delivering timely insights.}
      \resumeItem{Optimized a JSON-based caching mechanism to reduce API calls by 40\% while sustaining high data throughput, improving system performance and scalability.}
      \resumeItem{Automated keyword detection for terms like Bitcoin and Dogecoin with 15-minute interval checks, processing over 100 tweets per hour, increasing monitoring accuracy.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{EXTRACURRICULAR}
\resumeSubHeadingListStart
  \resumeSubheading
    {Core Member}{Bhopal, Madhya Pradesh}
    {IoT Club, VIT Bhopal}{June 2023 -- May 2024}
    \resumeItemListStart
      \resumeItem{Organized 5 campus events focused on IoT awareness, technical skills, and peer collaboration.}
      \resumeItem{Fostered innovation and learning by coordinating with cross-functional student teams.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
